Clustering: A pipeline to analyse time-course gene expression data

### 2019-03-05 scripts/03_clustering.Rmd
FIX pushd cannot be used in makefiles

```{r filter_genes}
if(filter_genes){
    # First, filter out any genes that doesn't have a log fold change of at
    # least 2
    # XXX I should actually filter on the max, but it is broken right now.
    lfc_col_to_keep = colnames(de_analysis)[
	grepl("-lfc_max", colnames(de_analysis))]
    de_analysis = de_analysis[rowSums(abs(de_analysis[, lfc_col_to_keep]) > 2) > 0, ]

>>>>

The next step is to perform clustering.

```{r filter_genes}
if(filter_genes){
    # First, filter out any genes that doesn't have a log fold change of at
    # least 2 at at least one of the time points.
    lfc_col_to_keep = colnames(de_analysis)[
	grepl("-lfc_max", colnames(de_analysis))]
    de_analysis = de_analysis[rowSums(abs(de_analysis[, lfc_col_to_keep]) > 2) > 0, ]
